\documentclass[11pt]{article}
\usepackage{coling2018}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\title{Deconvolution for linguistic analysis}

\author{
L. Vanni\textsuperscript{1}, V. Elango\textsuperscript{2}, D. Longrée\textsuperscript{3}, D. Mayaffre\textsuperscript{1}, F. Precioso\textsuperscript{2}, M. Ducoffe\textsuperscript{2}\\
  \textsuperscript{1} Univ. Nice Sophia Antipolis - I3S, UMR UNS-CNRS 7271 06900 Sophia Antipolis, France \\
  \{lvanni, mayaffre\}@unice.fr \\
  \textsuperscript{2} Univ. Nice Sophia Antipolis - BCL, UMR UNS-CNRS 7320 - 06357 Nice CEDEX 4, France \\
  \{ducoffe, precioso\}@unice.fr - ecveer@gmail.com \\
  \textsuperscript{3} Univ. Liège - L.A.S.L.A, Bélgique \\
  dominique.longree@uliege.be\\}
\date{}

\begin{document}
\maketitle



\begin{abstract}
  This document contains the instructions for preparing a paper submitted
  to COLING-2018 or accepted for publication in its proceedings. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers. Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\input{1_intro}

\input{2_related}

\input{3_comparison}

\input{4_motif}

\input{5_conclusion}

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}
